### 2016-08-31 version0.0/intro0.01.tex
Adding about the origin of 21 cm emission.

The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state. 
The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
The energy of the anti-parallel mode is slightly less than the parallel mode.
Since atoms always tend to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
The large amount of hydrogen atoms compensates for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
Observation of the \hi~atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.

@@

\begin{figure}
\centering
\includegraphics[width=16cm]{../image_intro/imf.png}
\small
\caption[Comparing stellar initial mass functions]{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex, power of 10, versus mass, normalized so that the integral under each curve is unity. The mass ranges from 0.1 to 120~M$_\odot$. Adopted from~\cite{Baldry03}.} 
\label{fig: imf}
\end{figure}

@@

\subsubsection{Resolved Star Formation Indicators}
The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$~kpc of the Solar System. 
The number of YSOs can be converted to SFR using: 
\begin{equation}
\m {SFR}(YSO) = N_{yso} <M>/\tau 
\end{equation}
where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
$<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
$\tau$ is the lifetime of the YSO  $\tau \sim 2$~Myr~\citep{Evans09}. 
Since our current devices cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.

>>>>

The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state, which is the state of lowest energy.
Due to a coupling between the total angular momentum of the electron and the angular momentum (spin) of the nucleus, the ground state of hydrogen atom splits into two states that are separated in energy by an amount of 1420.40~MHz.
This splitting is referred to as the hyperfine structure. 
The electron can be in either of the two aforementioned states. 
These states are very stable and the transition between them is forbidden, with a transition rate of $2.5\times10^{-15}\mathrm{s}^{-1}$.
This means that one would expect this transition to naturally happen once every ten million years.
%The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
%The energy of the anti-parallel mode is slightly less than the parallel mode.
%Since atoms always tend to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
%However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
However, the large amounts of hydrogen atoms in these atomic clouds compensate for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
Observation of the \hi~atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.

@@

\begin{figure}
\centering
\includegraphics[width=15.5cm]{../image_intro/imf.png}
\small
\caption[Comparing stellar initial mass functions]{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex, power of 10, versus mass, normalized so that the integral under each curve is unity. The mass ranges from 0.1 to 120~M$_\odot$. Adopted from~\cite{Baldry03}.} 
\label{fig: imf}
\end{figure}

@@

\subsubsection{Resolved Star Formation Indicators}
The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$~kpc of the Solar System. 
The number of YSOs can be converted to SFR using: 
\begin{equation}
{\m SFR}(YSO) = N_{yso} <M>/\tau 
\end{equation}
where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
$<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
$\tau$ is the lifetime of the YSO  $\tau \sim 2$~Myr~\citep{Evans09}. 
Since our current devices cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.
